%-------------------------
% Master Resume - GCP, AWS, Distributed Systems & E-Commerce
% Author: Karanvir (Karan) Khanna
% Targeted for: Google / High-Scale ML Engineering
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\fancyfoot[C]{\thepage}

% Optimization for max content
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.6in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-.6in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

\pdfgentounicode=1

%---------- Custom commands ----------
\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textbf{\small#3} & \small #4 \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%---------- HEADING ----------
\begin{center}
    \textbf{\Huge \scshape Karanvir (Karan) Khanna} \\ \vspace{2pt}
    \small \textbf{Machine Learning Engineer · Cloud Architect (GCP/AWS) · E-Commerce Optimization} \\ \vspace{4pt}
    \small 416-347-3761 $|$
    \href{mailto:karanvir.khanna@mail.utoronto.ca}{\underline{karanvir.khanna@mail.utoronto.ca}} $|$
    \href{https://bit.ly/karan2026}{\underline{Personal Website}} $|$
    \href{https://github.com/Karanvir1729}{\underline{GitHub}} $|$
    \href{https://linkedin.com/in/karan-khanna-b7013b24b}{\underline{LinkedIn}}
\end{center}

%----------- EDUCATION & PROFILE -----------
\section{Education \& Professional Profile}
  \small{
    \textbf{Profile:} \textbf{Hack the North Winner (2025)} and ML Engineer with deep expertise in \textbf{GCP-native AI solutions} and \textbf{distributed systems}. Proven track record in building high-availability e-commerce platforms using \textbf{Cassandra}, \textbf{Redis}, and \textbf{Kubernetes}. Expert in transformer fine-tuning, demand forecasting, and mathematical optimization (SCIP/MINLP). \\ \vspace{3pt}
    \textbf{Availability:} Graduating April 2026 — Available for immediate start (Full-time).
  }
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Toronto}{Apr. 2026}
      {Honours Bachelor of Science in Computer Science}{CGPA: 3.7/4.0 · Dean's List}
      \resumeItemListStart
        \resumeItem{\textbf{Key Coursework:} Neural Networks \& Deep Learning (CSC413), Fundamentals of ML (CSC311), Distributed Systems, Algorithm Design, Linear Algebra, Probability \& Statistics, Operating Systems.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%----------- TECHNICAL SKILLS -----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \item \small{
    \textbf{Cloud \& Infrastructure:} GCP (BigQuery, Pub/Sub, Vertex AI), AWS (EC2, Lambda, S3), Docker, Kubernetes, Terraform, NGINX, GitHub Actions (CI/CD) \\
    \textbf{Databases \& Caching:} Cassandra (Wide-column), Redis (In-memory), Firestore (NoSQL), PostgreSQL, MongoDB, Pinecone (Vector DB) \\
    \textbf{Machine Learning:} PyTorch, TensorFlow, Hugging Face, CodeT5, Gemini 1.5 Pro, Prophet, Scikit-learn, XGBoost \\
    \textbf{E-Commerce Stack:} SAP Business One, Moneris API, OMS/WMS Logic, Auth0, Shopify API, Stripe, Amazon SP-API \\
    \textbf{Optimization:} SCIP, CPLEX, Pyomo, Mixed-Integer Nonlinear Programming (MINLP), Gurobi \\
    \textbf{Languages:} Python, TypeScript/Node.js, SQL, C/C++, Java, GDScript, Bash, Go
  }
\end{itemize}

%----------- EXPERIENCE -----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Machine Learning Engineer \& E-Commerce Architect}{Jun. 2024 -- Sept. 2025}
      {IPPINKA}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Architected an \textbf{event-driven} inventory and order sync platform on \textbf{GCP} using \textbf{Pub/Sub} and \textbf{Cloud Functions} to propagate real-time updates across OMS/WMS, Shopify, and Amazon marketplaces for 5,000+ SKUs.}
        \resumeItem{Engineered a \textbf{BigQuery} analytics pipeline over 10+ years of sales and operations data; trained and deployed \textbf{demand forecasting} models to reduce stockouts and improve inventory turnover by 23\%.}
        \resumeItem{Built \textbf{semantic product search} using \textbf{Vertex AI embeddings} and ranking heuristics; improved query relevance and increased search-to-cart conversion by 18\%.}
        \resumeItem{Implemented a low-latency metadata layer with \textbf{Firestore} and caching patterns to replace a legacy Sheets-based backend, cutting API latency by 35\% and improving reliability under burst traffic.}
        \resumeItem{Developed personal \textbf{AI automation workflows} (including a Gemini-based documentation agent) that enabled a sustained **average productivity of 7+ hours daily active coding time (3.5x average dev)**, significantly accelerating delivery.}
        \resumeItem{Built an automated \textbf{purchase-order optimizer} in Pyomo using \textbf{SCIP/CPLEX} to solve supplier constraints (MOQ, lead time, budget) and generate feasible, cost-efficient bulk orders.}
        \resumeItem{Developed Python middleware for \textbf{SAP Business One} and \textbf{Moneris} to automate reconciliation, invoicing, and near real-time financial reporting.}
        \resumeItem{Designed and shipped a \textbf{customer loyalty and points system} integrated with \textbf{Auth0} for secure identity and personalized marketing triggers.}
        \resumeItem{Mentored 3 developers on ML and production readiness, and authored technical documentation for data pipelines and solver orchestration.}
      \resumeItemListEnd

    \resumeSubheading
      {AI/ML Engineer – Data Governance}{May 2023 -- Oct. 2023}
      {KPMG LLP}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Developed \textbf{LLM-powered assistants} using OpenAI and Gemini APIs to automate data governance workflows, reducing manual compliance review time by 60\%.}
        \resumeItem{Designed \textbf{GCP and Azure ML architectures} for enterprise-scale PII detection and automated classification across multi-cloud data lakes.}
        \resumeItem{Implemented \textbf{similarity matching pipelines} for Master Data Management (MDM) using fuzzy matching and Levenshtein distance to create "Golden Records" from noisy data.}
        \resumeItem{Authored KPMG's Data Governance Playbook with ML-enhanced automation strategies; presented findings to 50+ enterprise clients.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%----------- ML PROJECTS -----------
\section{Machine Learning Projects}
  \resumeSubHeadingListStart

    \resumeProjectHeading{\textbf{Tarazoo (Hack the North Winner 2025)} \href{https://github.com/ishan-singh-3005/tarazoo}{\underline{[Repo]}} $|$ \emph{GCP, FastAPI, PyTorch, Prophet/ARIMA, SCIP, Redis, Cassandra}}{2025--2026}
      \resumeItemListStart
        \resumeItem{Co-built an \textbf{AI-powered inventory optimization SaaS} for Shopify merchants, live at \href{https://www.tarazoo.shop}{\underline{tarazoo.shop}}; designed for production-grade scale with stateless APIs and asynchronous job execution.}
        \resumeItem{Implemented \textbf{demand forecasting} pipeline (Prophet, ARIMA) with automated backtesting and retraining triggers; produced SKU-level forecasts feeding downstream optimization and reorder recommendations.}
        \resumeItem{Built \textbf{constraint-based purchase order generation} with \textbf{SCIP} to solve real-world procurement constraints (MOQ, lead times, budget, stockout risk), generating feasible POs optimized for cash flow and service level.}
        \resumeItem{Integrated \textbf{NLP review intelligence} using transformer embeddings for sentiment/topic signals to adjust demand priors and surface product-quality drivers in merchant analytics.}
        \resumeItem{Deployed on \textbf{GCP Cloud Run} with containerized microservices; used \textbf{Pub/Sub}-style eventing patterns for decoupled ingestion, forecasting, and optimization stages, enabling horizontal scaling under burst traffic.}
        \resumeItem{Engineered low-latency state and feature access with \textbf{Redis} caching and high-write telemetry storage patterns (clickstream and events), enabling near real-time dashboards and model monitoring.}
      \resumeItemListEnd

    \resumeProjectHeading{\textbf{Python-to-Java Code Translator} \href{https://github.com/Karanvir1729/Python-to-Java-Code-Translator}{\underline{[Repo]}} $|$ \emph{PyTorch, Hugging Face, CodeT5, CUDA}}{2025}
      \resumeItemListStart
        \resumeItem{Fine-tuned a \textbf{CodeT5 transformer} on curated Python$\rightarrow$Java pairs with a reproducible training pipeline (tokenization, batching, mixed precision, checkpointing) for neural code translation.}
        \resumeItem{Implemented evaluation harness using \textbf{BLEU/CodeBLEU} plus compile-and-run checks; achieved \textbf{78\% compilation rate} on translated outputs and documented failure modes (types/imports/APIs).}
        \resumeItem{Built inference workflow for scalable serving: batched generation, deterministic decoding options, and post-processing for syntax/format normalization to improve compilation stability.}
      \resumeItemListEnd

    \resumeProjectHeading{\textbf{GuardianCruise – Driver Safety AI} \href{https://github.com/Karanvir1729/GuardianCruise}{\underline{[Repo]}} $|$ \emph{OpenCV, Python, ML Classification, Cohere}}{2024}
      \resumeItemListStart
        \resumeItem{Built a \textbf{real-time CV pipeline} (OpenCV) for driver monitoring: eye aspect ratio tracking, yawn detection, and distraction cues with on-frame temporal smoothing for stability.}
        \resumeItem{Trained and integrated an \textbf{ML classifier} for driver state and impairment risk; used an \textbf{LLM-based alerting layer} (Cohere) to generate context-aware interventions and escalation logic.}
      \resumeItemListEnd

    \resumeProjectHeading{\textbf{ML Boilerplates Library} \href{https://github.com/Karanvir1729/ML_boilerPlates}{\underline{[Repo]}} $|$ \emph{PyTorch, scikit-learn, Reproducible Training}}{2025}
      \resumeItemListStart
        \resumeItem{Created a \textbf{24+ model} implementation library covering supervised, unsupervised, and embedding workflows with consistent training loops, metrics, and experiment structure.}
        \resumeItem{Authored technical guides and decision trees for model selection, feature engineering, and evaluation, optimizing for rapid iteration and production handoff.}
      \resumeItemListEnd

    \resumeProjectHeading{\textbf{Tormented by Lights – Adaptive AI Game} \href{https://karanvir1729.itch.io/tormented-by-lights}{\underline{[Game]}} $|$ \emph{Godot, GDScript, Object Pooling}}{2024}
      \resumeItemListStart
        \resumeItem{Built a \textbf{Game Jam winner} (2D platformer) featuring a custom \textbf{Dynamic Difficulty Adjustment (DDA)} engine that modulates obstacle speed and spawn density using a PID controller based on player reaction time.}
        \resumeItem{Implemented efficient \textbf{object pooling} and a deterministic \textbf{physics state machine} in GDScript to handle collision detection and memory management, ensuring consistent 60FPS on web builds.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%----------- RESEARCH -----------
\section{Research Experience}
  \resumeSubHeadingListStart
    \resumeProjectHeading{\textbf{Matroid Theory \& Polytope Optimization} \href{https://github.com/Karanvir1729/MatriodResearch}{\underline{[Repo]}} $|$ \emph{University of Toronto}}{May 2023 -- Sep. 2023}
      \resumeItemListStart
        \resumeItem{Conducted research on \textbf{volume estimation of matroid polytopes} under Prof. Ahmed Ashraf, establishing links between combinatorial geometry and \textbf{loss landscapes} in high-dimensional optimization.}
        \resumeItem{Modeled \textbf{submodular set functions} as polytope constraints to analyze \textbf{greedy algorithm convergence}; findings have theoretical implications for \textbf{active learning} and \textbf{feature selection} in efficient ML.}
        \resumeItem{Applied \textbf{Hepp bounds} to estimate volumes, validating conjectures in SageMath that bridge discrete structures with \textbf{continuous relaxation methods} used in neural architecture search.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%----------- CERTIFICATIONS & AWARDS -----------
\section{Certifications \& Awards}
  \resumeSubHeadingListStart
    \resumeItem{\textbf{Hack the North Winner (2025)} — Shopify Challenge: AI Shopping with Computer Vision \& Optimization.}
    \resumeItem{\textbf{Invited to YCombinator (YC) Dinner} — Selected for exclusive founder networking event (2025).}
    \resumeItem{\textbf{Dean's List Scholarship} — Awarded for academic excellence (2021--Present).}
    \resumeItem{\textbf{DAMA Certified Data Management Professional (CDMP)} — Associate Level (80\% Score).}
    \resumeItem{\textbf{DeerHacks Winner (2022)} — Best Usage of UiPath: Created NLP-powered Essay Generator.}
    \resumeItem{\textbf{Halton Game Jam Winner (2025)} · \textbf{UofT Hacks Runner-up (2023)}}
  \resumeSubHeadingListEnd

\end{document}